si: code and prose exploring Spatial Interaction models

### 2022-06-13 README.qmd
Update urls

<!-- badges: start -->
[![R-CMD-check](https://github.com/robinlovelace/si/workflows/R-CMD-check/badge.svg)](https://github.com/robinlovelace/si/actions)
<!-- badges: end -->

@@

```r
remotes::install_github("robinlovelace/si")
```

@@

As documented in the [si vignette](https://robinlovelace.github.io/si/articles/si.html), the function allows you to use any variable in the origin or destination data by joining all attributes onto the OD data frame, with column names appended with `origin` and `destination`.

@@

For details on what SIMs are and how they have been defined mathematically and in code from first principles, see the [`sims` vignette](https://robinlovelace.github.io/si/articles/sims-first-principles.html).

To dive straight into using {sim} to develop SIMs, see the [`si` Get started vignette](https://robinlovelace.github.io/si/articles/si.html).

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/Robinlovelace/simm/workflows/R-CMD-check/badge.svg)](https://github.com/Robinlovelace/simm/actions)
<!-- badges: end -->

@@

```r
remotes::install_github("Robinlovelace/simm")
```

@@

As documented in the [si vignette](https://robinlovelace.github.io/sim/articles/sim.html), the function allows you to use any variable in the origin or destination data by joining all attributes onto the OD data frame, with column names appended with `origin` and `destination`.

@@

For details on what SIMs are and how they have been defined mathematically and in code from first principles, see the [`sims` vignette](https://robinlovelace.github.io/sim/articles/simms-first-principles.html).

To dive straight into using {sim} to develop SIMs, see the [`si` Get started vignette](https://robinlovelace.github.io/sim/articles/sim.html).
